\LARGE \bf On the use of vehicle categorization and context information for messages forwarding in VANETs

### 2016-09-16 paperITSC.tex
vehicles and environment contextual information test commit

Dey \cite{dey2001} defines context as “any information that can be use to characterize the situation of an entity. An entity is a person, place, or an object that is considered relevant to the interaction between an user and an application, including the user and applications themselves.” A system that make use of this sort of information is called context-aware system. Such systems achieve improvements in the quality of information and providing better services to the user. Context-aware systems are adaptable to  different situations, or context, without user intervention \cite{baldauf2007}.

By utilization the embedded sensors, a smart vehicle can produce rich context information. The context information about vehicle contains speed, direction, wheel friction, acceleration and position of the vehicle. Furthermore, a smart car would monitor its environment. The context information about environment can be divided into static (e.g., road signs, number of lanes), and dynamic (e.g., wind speed, range of visibility, chances of rain). Using context information of the vehicle or environment make it possible to detect or prevent hazardous situations. Moreover, the context can also be useful in the knowledge distribution over a vehicular network \cite{tocadas2010}.

An example of network that could make use of context information are the opportunistic networks, which take advantage of opportunistic encounters (not scheduled) to exchange data and share contextual information  \cite{geoopp2014}. Being aware of its neighbors and message destination position, a node can forward incoming messages towards the destination, by selecting the node that is geographically closer to the destination \cite{gpsr2000}. This way, the message could be forwarded accurately by using information about immediate neighbors only \cite{magf2009}.

The \autoref{context} shows some context information, regarding the \emph{driver}, the \emph{environment} and the \emph{vehicles}. This context information can be use to improve VANETs applications, such as advertising and entertainment. Some possible use cases are: a) sending warning message to the neighborhood about a reckless and fatigued driver; b) disseminating context-aware services advertisements to the near-by drivers; c) alerting drivers about traffic density and road conditions.

>>>>

Dey \cite{dey2001} defines context as “any information that can be used to characterize the situation of an entity. An entity is a person, place, or an object that is considered relevant to the interaction between a user and an application, including the user and applications themselves.” A system that makes use of this sort of information is called context-aware system. Such systems achieve improvements in the quality of information and providing better services to the user. Context-aware systems are adaptable to  different situations, or context, without user intervention \cite{baldauf2007}.

By utilization the embedded sensors, a smart vehicle can produce rich context information. The context information about vehicle contains speed, direction, wheel friction, acceleration and position of the vehicle. Furthermore, a smart car would monitor its environment. The context information about the environment can be divided into static (e.g., road signs, number of lanes), and dynamic (e.g., wind speed, range of visibility, chances of rain). Using context information of the vehicle or environment make it possible to detect or prevent hazardous situations. Moreover, the context can also be useful in the knowledge distribution over a vehicular network \cite{tocadas2010}.

An example of a network that could make use of context information are the opportunistic networks, which take advantage of opportunistic encounters (not scheduled) to exchange data and share contextual information  \cite{geoopp2014}. Being aware of its neighbors and message destination position, a node can forward incoming messages towards the destination, by selecting the node that is geographically closer to the destination \cite{gpsr2000}. This way, the message could be forwarded accurately by using information about immediate neighbors only \cite{magf2009}.

The \autoref{context} shows some context information, regarding the \emph{driver}, the \emph{environment} and the \emph{vehicles}. This context information can be use to improve VANETs applications, such as advertising and entertainment. Some possible use cases are a) sending warning message to the neighborhood about a reckless and fatigued driver; b) disseminating context-aware services advertisements to the nearby drivers; c) alerting drivers about traffic density and road conditions.
